---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(lme4)
```

Loading data and converting it to a tibble

```{r}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

Excluding Subjects

```{r}
all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6" & subject_id!="5ce1372c55fe0d001869c8d8" & subject_id!="5f47d860b56e68220cb86be1" & subject_id!="607eaf87ac02229ef4fa8f4a" & subject_id!="5d30857eb2f0ad00163470f3" & subject_id!="5e272684f205790453c2c4b8" & subject_id!="5f5b5881b17fa72756b8ff2a" & subject_id!="5fae5291ec402509e2885604")
```

Convert data to long format for gaze measurements

```{r}
task.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, time_elapsed, trial_index, response, rt, webgazer_data, webgazer_targets) %>%
  unnest(webgazer_data) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c('#face1', '#face2'), names_sep = ".")
```

Add condition information

```{r}
task.data <- task.data %>%
  mutate(task = if_else(study_id == '60748d36577623e2677865c6', "Attractiveness", "Roundness"))
```

Compute average trial length

```{r}
response.time.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, study_id, trial_index, response, rt)
```

```{r}
rt.summary <- response.time.data %>%
  summarize(M=mean(rt), SD=sd(rt))

cutoff.time <- rt.summary$M - rt.summary$SD
#cutoff.time <- 1670

rt.summary
```


# Eye Gaze Analysis

Normalize time to time until decision

```{r}
task.data <- task.data %>%
  mutate(time_until_decision = rt - t)
```

Normalize t measurement to time before decision

```{r}
task.data <- task.data %>%
  filter(time_until_decision <= cutoff.time)
```

Add in-the-box info

```{r}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

```{r}
task.data <- task.data %>%
  mutate(in.left.box = in.box(x,y,`#face1.left`,`#face1.right`,`#face1.top`,`#face1.bottom`,0)) %>%
  mutate(in.right.box = in.box(x,y,`#face2.left`,`#face2.right`,`#face2.top`,`#face2.bottom`,0)) %>%
  mutate(in.target.box = if_else(response == 'a', in.left.box, in.right.box)) %>%
  mutate(in.other.box = if_else(response == 'a', in.right.box, in.left.box))
```

Bin the time by 50ms

```{r}
task.data <- task.data %>%
  mutate(time.window = floor(time_until_decision/50)*50)
```

Summarize by time window

```{r}
summary.gaze.view.subject <- task.data %>%
  filter(in.target.box == TRUE | in.other.box == TRUE) %>%
  group_by(subject_id, time.window, task) %>%
  summarize(prop.in.target.subject = mean(in.target.box))
```
```{r}
summary.gaze.view <- summary.gaze.view.subject %>%
  group_by(time.window, task) %>%
  summarize(prop.in.target = mean(prop.in.target.subject), se = sd(prop.in.target.subject)/sqrt(n()))
```

KS Test?

```{r}
ks.test(summary.gaze.view %>% filter(task == "Attractiveness") %>% pull(prop.in.target),
         summary.gaze.view %>% filter(task == "Roundness") %>% pull(prop.in.target))
```

<!--re-reading the paper, I think the KS test is over fitted parameters? -RR-->

```{r}
ggplot(summary.gaze.view, aes(x=time.window, y=prop.in.target, ymin=prop.in.target-se, ymax=prop.in.target+se, color=task, fill=task))+
  geom_ribbon(color=NA, alpha=0.3)+
  geom_line()+
  scale_x_reverse()+
  theme_classic()+
  labs(x="Time until decision (ms)", y="Proportion of gaze in target", color="Task", fill="Task")
```


Fit sigmoid curve

```{r}
attractiveness.curve <- summary.gaze.view %>% filter(task != "Roundness")
fit <- nls(prop.in.target ~ MaxP + (MinP - MaxP)/(1+(time.window/InfP)^Slope), data = attractiveness.curve, start=list(MaxP=0.9,MinP=0.5,InfP=-500,Slope=-1))
```


alternative analyses with mixed effects models:
<!--added these when working on CDS abstract -RR-->

```{r}
summary.gaze.view.subject$time.window.c<-scale(summary.gaze.view.subject$time.window, center=T, scale=F )
summary(lmer(prop.in.target.subject ~ task*time.window.c + (1 + time.window.c|subject_id), data = summary.gaze.view.subject))
```

regression with lag predictor

```{r}
summary.gaze.view.subject = summary.gaze.view.subject %>% 
  group_by(subject_id,task) %>% 
  mutate(lag1_prop = lag(prop.in.target.subject))
```

```{r}
summary(lmer(prop.in.target.subject ~ task + lag1_prop + (1 + lag1_prop |subject_id), data = summary.gaze.view.subject))
```