---
title: "AS-polling-rate"
output: html_document
---

```{r AS-polling-rate, include=FALSE}
library(dplyr)
library(jsonlite)
library(tidyr)
library(ggplot2)


knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```


```{r load-data-E1}
data.files <- list.files('../group-a/data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)

all.data <- all.data %>%
  mutate(subject_id = factor(subject_id))

task.data <- all.data %>%
  filter(verb_type %in% c("restricting", "non-restricting")) %>%
  select(subject_id, stimulus, response, verb_type, webgazer_data, webgazer_targets) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(`#scenes`) %>%
  select(-x,-y) %>%
  unnest(webgazer_data) %>%
  mutate(gaze.x.percent = (x - left) / width * 100) %>%
  mutate(gaze.y.percent = (y - top) / height * 100)
```


```{r calculate-polling-rate-E1}
polling.rate.E1 <- task.data %>%
  select(subject_id, stimulus, t) %>%
  group_by(subject_id, stimulus) %>%
  summarize(samples = n(),
            seconds = (max(t) - min(t)) / 1000,
            samples_per_second = samples / seconds) %>%
  group_by(subject_id) %>%
  summarize(M = mean(samples_per_second))
```

```{r load-data-E2}
data.files <- list.files('../group-b/data', full.names = TRUE, pattern=".json")

data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})

all.data <- bind_rows(data.tables)

task.data <- all.data %>%
  filter(!is.na(relation)) %>%
  select(subject_id, trial_index, stimulus, relation, quadrant, rt, correct_response, response, webgazer_data, webgazer_targets) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(`#screen`) %>%
  select(-top,-left,-x,-y,-bottom,-right) %>%
  unnest(webgazer_data)
```

```{r calculate-polling-rate-E2}
polling.rate.E2 <- task.data %>%
  select(subject_id, trial_index, t) %>%
  group_by(subject_id, trial_index) %>%
  summarize(samples = n(),
            seconds = (max(t) - min(t)) / 1000,
            samples_per_second = samples / seconds) %>%
  group_by(subject_id) %>%
  summarize(M = mean(samples_per_second))
```

```{r load-data-E3}
data.files <- list.files('../group-c/data', full.names = TRUE, pattern=".json")

data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)

study.id.day.1.group.1 <- "6062337f1a63a6788185d0e3"
study.id.day.1.group.2 <- "607de170bb44b7e25174421f"
study.id.day.2.group.1 <- "606233c0e42b980319b6a18e"
study.id.day.2.group.2 <- "607de2837874a824e2e8c6ec"

all.data <- all.data %>%
  mutate(day = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.1.group.2), 1, 2)) %>%
  mutate(group = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.2.group.1), 1, 2))

data.day.1 <- all.data %>% filter(day == 1)
data.day.2 <- all.data %>% filter(day == 2)

eyetracking.data <- data.day.1 %>%
  filter(phase == "part2") %>%
  select(subject_id, trial_index, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c("#left-img", "#right-img"), names_sep=".") %>%
  tidyr::unnest(webgazer_data) %>% 
  filter(subject_id != "5b807fb716aa4400016a6f8e") # has two sets of eyetracking data
```

```{r calculate-polling-rate-E3}
polling.rate.E3 <- eyetracking.data %>%
  select(subject_id, trial_index, t) %>%
  group_by(subject_id, trial_index) %>%
  summarize(samples = n(),
            seconds = (max(t) - min(t)) / 1000,
            samples_per_second = samples / seconds) %>%
  group_by(subject_id) %>%
  summarize(M = mean(samples_per_second))
```

```{r load-data-E4}
data.files <- list.files('../group-d/data/run-2', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)


task.data <- all.data %>%
  dplyr::filter(compatibility != 'NA', compatibility != 'filler') %>%
  dplyr::select(subject, trial_index, rt, images, webgazer_data, mouse_events, compatibility, audio, target_instrument, target_animal, webgazer_targets)

# Add a column that uniquely identifies the combination of images and audio shown on the screen
trialID.data <- task.data %>%
  group_by(audio, images) %>%
  slice(1) %>%
  select(audio, images) %>%
  ungroup() %>%
  mutate(trialID = 1:n())

task.data <- task.data %>%
  left_join(trialID.data)

eyetracking.data <- task.data %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c(`#jspsych-free-sort-draggable-0`, `#jspsych-free-sort-draggable-1`, `#jspsych-free-sort-draggable-2`, `#jspsych-free-sort-draggable-3`), names_sep=".") %>%
  unnest(webgazer_data)

```

```{r calculate-polling-rate-E4}
polling.rate.E4 <- eyetracking.data %>%
  select(subject, trialID, t) %>%
  group_by(subject, trialID) %>%
  summarize(samples = n(),
            seconds = (max(t) - min(t)) / 1000,
            samples_per_second = samples / seconds) %>%
  group_by(subject) %>%
  summarize(M = mean(samples_per_second))
```

```{r load-data-E5}
data.files <- list.files('../group-e/data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})

all.data <- bind_rows(data.tables)

all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6")

# Code condition information
all.data <- all.data %>%
  mutate(task = if_else(study_id == '60748d36577623e2677865c6', "Attractiveness", "Roundness"))

# Convert data to long format for gaze measurements
task.data <- all.data %>%
  filter(response=="a" | response=="d") %>%
  select(subject_id, task, time_elapsed, trial_index, response, rt, webgazer_data, webgazer_targets) %>%
  unnest(webgazer_data) %>%
  tidyr::unpack(webgazer_targets) %>%
  tidyr::unpack(c('#face1', '#face2'), names_sep = ".")
```

```{r calculate-polling-rate-E5}
polling.rate.E5 <- task.data %>%
  select(subject_id, trial_index, t) %>%
  group_by(subject_id, trial_index) %>%
  summarize(samples = n(),
            seconds = (max(t) - min(t)) / 1000,
            samples_per_second = samples / seconds) %>%
  group_by(subject_id) %>%
  summarize(M = mean(samples_per_second))
```

```{r combine-polling-rates}
polling.rate.all <- polling.rate.E1 %>%
  mutate(study = "E1") %>%
  bind_rows(polling.rate.E2 %>% mutate(study = "E2")) %>%
  bind_rows(polling.rate.E3 %>% mutate(study = "E3")) %>%
  bind_rows(polling.rate.E4 %>% mutate(study = "E4", subject_id = subject) %>% select(-subject)) %>%
  bind_rows(polling.rate.E5 %>% mutate(study = "E5"))

within.1Hz.of.target <- polling.rate.all %>%
  mutate(within.1Hz = if_else(M >= 29 & M <= 31, 1, 0)) %>%
  pull(within.1Hz) %>%
  mean() %>%
  round(digits=3)*100
```

We used a fork of the `webgazer.js` library for webcam eye-tracking
[@papoutsaki2016webgazer], implemented in `jsPsych`, a Javascript
library for running behavioral experiments in a web browser
[@deleeuwJsPsychJavaScriptLibrary2015].[^1] Our fork included changes to
`webgazer.js` in order to improve data quality for experiments in which
the precise timing of stimulus onsets is relevant. Specifically, we
implemented a polling mode so that gaze predictions could be requested
at a regular interval, which improved the sampling rate considerably in
informal testing. We aimed for a 30Hz sampling rate in all experiments, 
which was achievable for about `r round(mean(polling.rate.all$M), digits=1` of the participants 
(Figure\ \@ref(fig:polling-rate-figure)).
This modification is similar to what Yang and Krajbich
[-@yang2021webcam] reported improved the sampling rate in their study of
webgazer. We also adjusted the mechanism for recording time stamps of
each gaze prediction, so that the time stamp reported by webgazer is
based on when the video frame is received and not when the computation
of the gaze point is finished.


```{r polling-rate-figure, include=TRUE, echo=FALSE, fig.cap="Achieved polling rate across all studies. We attempted to sample at 30Hz, which is a standard webcam refresh rate. The plurality of participants met this rate, but there was a long tail of slower rates."}
ggplot(polling.rate.all, aes(x = M)) +
  geom_histogram(bins=15) + 
  theme_bw() +
  theme(legend.position = "none") +
  labs(x = "Achieved polling rate (samples per second)", y = "") +
  theme(panel.grid=element_blank())
```
