---
title: "AS-repeat-calibration"
output: html_document
---

```{r AS-repeat-calibration, include=FALSE}
library(dplyr)
library(jsonlite)
library(tidyr)
library(ggplot2)


knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r recalibration-load-data-E1}
data.files <- list.files('../group-a/data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)

all.data <- all.data %>%
  mutate(subject_id = factor(subject_id)) 
```

```{r calculate-recalibration-rate-E1}
recalibration.rate.E1 <- all.data %>%
  filter(trial_type %in% c("webgazer-calibrate", "webgazer-validate")) %>%
  select(subject_id, phase) %>%
  group_by(subject_id) %>%
  summarize(recalibrated = "recalibration" %in% phase)
```

```{r recalibration-load-data-E2}
data.files <- list.files('../group-b/data', full.names = TRUE, pattern=".json")

data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})

all.data <- bind_rows(data.tables)
```

```{r calculate-recalibration-rate-E2}
recalibration.rate.E2 <- all.data %>%
  filter(trial_type %in% c("webgazer-calibrate", "webgazer-validate")) %>%
  select(subject_id, phase) %>%
  group_by(subject_id) %>%
  summarize(recalibrated = "recalibration" %in% phase)
```

```{r recalibration-load-data-E3}
data.files <- list.files('../group-c/data', full.names = TRUE, pattern=".json")

data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r calculate-recalibration-rate-E3}
recalibration.rate.E3 <- all.data %>%
  filter(trial_type %in% c("webgazer-calibrate", "webgazer-validate")) %>%
  select(subject_id, phase) %>%
  group_by(subject_id) %>%
  summarize(recalibrated = "recalibration" %in% phase)
```

```{r recalibration-load-data-E4}
data.files <- list.files('../group-d/data/run-2', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

```{r calculate-recalibration-rate-E4}
recalibration.rate.E4 <- all.data %>%
  filter(trial_type %in% c("webgazer-calibrate", "webgazer-validate")) %>%
  select(subject, phase) %>%
  group_by(subject) %>%
  summarize(recalibrated = "recalibration" %in% phase)
```

```{r recalibration-load-data-E5}
data.files <- list.files('../group-e/data', full.names = TRUE, pattern=".json")
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  return(data.table)
})

all.data <- bind_rows(data.tables)

all.data <- all.data %>% filter(subject_id!="603ea6a51c38def3e4140ba6")

```

```{r calculate-recalibration-rate-E5}
recalibration.rate.E5 <- all.data %>%
  filter(trial_type %in% c("webgazer-calibrate", "webgazer-validate")) %>%
  select(subject_id, phase) %>%
  group_by(subject_id) %>%
  summarize(recalibrated = "recalibration" %in% phase)
```

```{r combine-recalibration-rates}
recalibration.rate.all <- recalibration.rate.E1 %>%
  mutate(study = "E1") %>%
  bind_rows(recalibration.rate.E2 %>% mutate(study = "E2")) %>%
  bind_rows(recalibration.rate.E3 %>% mutate(study = "E3")) %>%
  bind_rows(recalibration.rate.E4 %>% mutate(study = "E4", subject_id = subject) %>% select(-subject)) %>%
  bind_rows(recalibration.rate.E5 %>% mutate(study = "E5"))

recalibration.rate <- round(100* mean(recalibration.rate.all$recalibrated), digits=2)
```


<!--took paragraph below from group D's methods -->

When participants began the experiment, they were notified the webcam
would be used for eye tracking but no video would be saved. They were
asked to remove glasses if possible, close any other tabs or apps, turn
off notifications, and make sure their face was lit from the front. The
webcam's view of the participant popped up on the screen, and
participants were asked to center their face in the box and keep their
head still. The experiment window then expanded to full screen, and
participants began the eye-tracking calibration.

During the calibration, dots appeared on the screen one at a time in
different locations, and the participants had to fixate them and click
on each one. Once they clicked on a dot, it would disappear and a new
one would appear in a different location on the screen. The locations of
calibration dots were specific to each experiment (details below) and
appeared in the areas of the screen where the visual stimuli would
appear during the main task in order to ensure that eye movements were
accurately recorded in the relevant regions of interest. After the
calibration was completed, the validation began. Participants were asked
to go through the same steps as the calibration, except that they only
fixated the dots as they appeared in different locations on the screen.
If accuracy on the validation was too low (fewer than 50% of looks
landed within a 200 px radius of the validation points),
participants were given an opportunity to re-start the calibration and
validation steps. Across all of the experiments reported, `r recalibration.rate`%
of participants required recalibration. However, even participants with low 
calibration accuracy were allowed to complete the experiment, because we 
specifically wanted to study the consequences of low calibration accuracy.

Upon finishing calibration, participants were reminded to keep their head still for the remainder of the study.
