---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

Loading data and converting it to a tibble

```{r}
data.files <- list.files('data', full.names = TRUE)
data.tables <- lapply(data.files, function(file){
  data.table <- fromJSON(file)
  data.table$response <- as.character(data.table$response)
  return(data.table)
})
all.data <- bind_rows(data.tables)
```

Split Part 1 and Part 2 data

```{r}
study.id.day.1.group.1 <- "6062337f1a63a6788185d0e3"
study.id.day.1.group.2 <- "607de170bb44b7e25174421f"
study.id.day.2.group.1 <- "606233c0e42b980319b6a18e"
study.id.day.2.group.2 <- "607de2837874a824e2e8c6ec"

all.data <- all.data %>%
  mutate(day = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.1.group.2), 1, 2)) %>%
  mutate(group = if_else(study_id %in% c(study.id.day.1.group.1, study.id.day.2.group.1), 1, 2))

data.day.1 <- all.data %>% filter(day == 1)
data.day.2 <- all.data %>% filter(day == 2)
```

Select the eyetracking data

```{r}
eyetracking.data <- data.day.1 %>%
  filter(phase == "part2") %>%
  select(subject_id, webgazer_data, webgazer_targets, left_image_new, right_image_new, right_image, left_image) %>%
  unpack(webgazer_targets) %>%
  unpack(c("#left-img", "#right-img"), names_sep=".") %>%
  unnest(webgazer_data)
```

Add ROI information

```{r}
in.box <- function(x, y, left, right, top, bottom, padding){
  is.in.the.box <- x >= left - padding & x <= right + padding & y >= top - padding & y <= bottom + padding
  return(is.in.the.box)
}
```

```{r}
eyetracking.data <- eyetracking.data %>%
  mutate(in.left.roi = in.box(x, y,`#left-img.left`, `#left-img.right`, `#left-img.top`, `#left-img.bottom`, 50))%>%
  mutate(in.right.roi = in.box(x, y,`#right-img.left`, `#right-img.right`, `#right-img.top`, `#right-img.bottom`, 50))%>%
  mutate(in.target.roi = if_else(left_image_new == TRUE, in.left.roi, in.right.roi))%>%
  mutate(in.distractor.roi = if_else(left_image_new == TRUE, in.right.roi, in.left.roi))
```

Get looking score (proportion of samples in the target ROI vs distractor ROI)

```{r}
looking.score.data <- eyetracking.data %>% 
  group_by(subject_id, right_image, left_image, right_image_new, left_image_new) %>%
  summarise(looking.score = if_else(sum(in.target.roi, in.distractor.roi) == 0, 0, sum(in.target.roi)/ sum(in.target.roi, in.distractor.roi))) %>%
  mutate(image = if_else(right_image_new, left_image, right_image))
```

Do subjects look at the new object more than the old object? (Is looking score statistically greater than 0.5?)

```{r}
t.test.data1 <- looking.score.data %>%
  group_by(subject_id) %>%
  summarize(M.looking.score = mean(looking.score))

t.test(t.test.data1$M.looking.score, mu = 0.5)
```

# Day 2 Performance

```{r}
day2.test.data <- data.day.2 %>%
  filter(task %in% c("recognition", "confidence")) %>%
  select(subject_id, image, old_or_new, correct, rt, response, task) %>%
  pivot_wider(names_from=task, values_from=c(correct, response, rt)) %>%
  select(-correct_confidence) %>%
  mutate(response_confidence = as.numeric(response_confidence))
```

Are people more confident after a correct response than an incorrect response?

```{r}
confidence.test.data <- day2.test.data %>%
  group_by(subject_id, correct_recognition) %>%
  summarize(M.confidence = mean(response_confidence))

subjects.100.percent.accurate <- day2.test.data %>%
  group_by(subject_id) %>%
  summarize(accuracy = mean(correct_recognition)) %>%
  filter(accuracy == 1) %>%
  pull(subject_id)

confidence.test.data.filtered <- confidence.test.data %>%
  filter(!subject_id %in% subjects.100.percent.accurate)

t.test(M.confidence ~ correct_recognition, data=confidence.test.data.filtered, paired=T)
```

Are people faster to make a correct response?

```{r}
rt.test.data <- day2.test.data %>%
  group_by(subject_id, correct_recognition) %>%
  summarize(M.rt = mean(rt_recognition))

rt.test.data.filtered <- rt.test.data %>%
  filter(!subject_id %in% subjects.100.percent.accurate)

t.test(M.rt ~ correct_recognition, data=rt.test.data.filtered, paired=T)
```

Does Looking Score Predict Confidence?

```{r}
looking.plus.behavioral <- left_join(looking.score.data, day2.test.data)

looking.confidence.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  group_by(subject_id) %>%
  summarize(pearson.r = cor(looking.score, response_confidence)) %>%
  mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

looking.confidence.correlations.subjects.filtered <- looking.confidence.correlations.subjects %>%
  filter(!is.na(pearson.r))
```

```{r}
hist(looking.confidence.correlations.subjects.filtered$r.to.z)
```

```{r}
t.test(looking.confidence.correlations.subjects.filtered$r.to.z)
```

```{r}
looking.rt.correlations.subjects <- looking.plus.behavioral %>%
  filter(correct_recognition == TRUE) %>%
  group_by(subject_id) %>%
  summarize(pearson.r = cor(looking.score, rt_recognition)) %>%
  mutate(r.to.z = .5*(log(1+pearson.r) - log(1 - pearson.r)))

looking.rt.correlations.subjects.filtered <- looking.rt.correlations.subjects %>%
  filter(!is.na(pearson.r))
```

```{r}
hist(looking.rt.correlations.subjects.filtered$r.to.z)
```

```{r}
t.test(looking.rt.correlations.subjects.filtered$r.to.z)
```


Plot of looking score vs. confidence

```{r}
ggplot(looking.plus.behavioral, aes(x=looking.score, y=response_confidence))+
  geom_point()
```